CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-02-02 codecheck-paper.tex
mention repro-packs alongside research compendia

\textbf{Should CODECHECK requirements not be more demanding?} \\
CODECHECK by design does not require authors to provide (and sustain) an
eternally functional workflow and neither suggests a specific software stack
or practical approach even if such suggestions, e.g.,~research compendia\footnote{\url{https://research-compendium.science/}}, are very valuable.
Creating something that anyone can reproduce has been called a 
fool's errand\footnote{\url{https://twitter.com/DougBlank/status/1135904909663068165?s=09}}
and we tend to agree.
However, the package of data, code, and documentation
collaboratively created by authors and codecheckers is a snapshot of a 
working analysis that greatly increases the likelihood of a successful 
reproduction and the possibility that a workflow can be extended by third parties in the future, as long as they have access
to suitable resources and matching skill set.
Concrete implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how to
create reproducibility packages.
The author-friendly ``low bar'' should not stay low forever, but cultural
change takes time and the encouragement and guidance that CODECHECK,
as part of the widely accepted peer review concept, can provide may
eventually allow the bar to be raised as high as possible, e.g.,~with
executable research compendia \cite{nust_opening_2017}, ``Whole Tales'' \cite{brinckman_computing_2018},
or continuous analysis \cite{beaulieu-jones_reproducibility_2017-1}.
However, considering that missing artefacts and lack of documentation
have repeatedly been identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}),
we would not underestimate the power of a simple check.
For example, ModelDB curation policies ensure that only one figure is manually reproduced \cite{mcdougal_reproducibility_2016}, but that has not limited the usefulness nor success of the platform.

>>>>

\textbf{Should CODECHECK requirements not be more demanding?} \\
CODECHECK by design does not require authors to provide (and sustain) an
eternally functional workflow and neither suggests a specific software stack
or practical approach even if such suggestions, e.g.,~research compendia or ``repro-packs''\footnote{See \url{https://research-compendium.science/} respectively \cite{barba_praxis_2018}.}, are very valuable.
Creating something that anyone can reproduce has been called a 
fool's errand\footnote{\url{https://twitter.com/DougBlank/status/1135904909663068165?s=09}}
and we tend to agree.
However, the package of data, code, and documentation
collaboratively created by authors and codecheckers is a snapshot of a 
working analysis that greatly increases the likelihood of a successful 
reproduction and the possibility that a workflow can be extended by third parties in the future, as long as they have access
to suitable resources and matching skill set.
Concrete implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how to
create reproducibility packages.
The author-friendly ``low bar'' should not stay low forever, but cultural
change takes time and the encouragement and guidance that CODECHECK,
as part of the widely accepted peer review concept, can provide may
eventually allow the bar to be raised as high as possible, e.g.,~with
executable research compendia \cite{nust_opening_2017}, ``Whole Tales'' \cite{brinckman_computing_2018},
or continuous analysis \cite{beaulieu-jones_reproducibility_2017-1}.
However, considering that missing artefacts and lack of documentation
have repeatedly been identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}),
we would not underestimate the power of a simple check.
For example, ModelDB curation policies ensure that only one figure is manually reproduced \cite{mcdougal_reproducibility_2016}, but that has not limited the usefulness nor success of the platform.
